Monte Carlo simulation of monetary transactions: \\ \normalsize{A simple model for wealth distribution} \\ \hrulefill\small{ FYS3150: Computational Physics }\hrulefill

### 2016-12-09 Project5/article/article.tex
Results 2/3

\usepackage[]{graphicx}
\usepackage{subcaption}
\usepackage[]{hyperref}
\usepackage[]{physics}
\usepackage[]{listings}
\usepackage[utf8]{inputenc}
\usepackage[dvipsnames]{xcolor}

@@

\subsection{Pareto distributions}

@@

@@

Figure \ref{fig:paramfig1} shows two different Pareto distrobutions plotted against a distribution at $\lambda = 0$.

@@

\begin{figure}
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=\textwidth]{../figures/5ac/5cLOGLOG_N500_varSavings.pdf}
  \caption{}
  \label{fig:logdistribution}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{../figures/5ac/omega.pdf}
  \caption{}
  \label{fig:straightline}
\end{subfigure}
\caption{Logarithmic plot wealth distribution from figure \ref{fig:distribution} (right), and }
\label{fig:logplot}
\end{figure}

\begin{figure}
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{../figures/5ac/5c_parameterization0.pdf}
  \caption{}
  \label{fig:paramfig1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{../figures/5ac/5c_parameterization09.pdf}
  \caption{}
  \label{fig:paramfig2}
\end{subfigure}
\caption{Parametrization}
\label{fig:paramfig}
\end{figure}

@@

@@

>>>>

\usepackage[]{graphicx}
\usepackage{subcaption}
\usepackage[toc,page]{appendix}
\usepackage[]{hyperref}
\usepackage[]{physics}
\usepackage[]{listings}
\usepackage[utf8]{inputenc}
\usepackage[dvipsnames]{xcolor}

@@

\subsection{Pareto distributions}
How the income and wealth of a population has been studied for a long time. Already in 1897, Vilfredo Pareto, sought to describe bot wealth and income distribution by power law probability distributions\cite{Pareto}. Pareto showed that the higher end of the distribution of money follows a distribution
\begin{equation}
\label{eq:paretodist}
w_m \propto m^{-1-\alpha}, \quad \alpha \in [1,2].
\end{equation}
Pareto's ``80-20 rule", that $20\%$ of the population controls $80\%$ of the wealth, corresponds to a certain value of $\alpha$. Today, a whole class of distributions similar to the one in equation \ref{eq:paretodist} are named after Pareto\cite{Arnold}.

@@

%% Problem a, b, c.

@@

Figure \ref{fig:paramfig1} shows two different Pareto distributions with $\alpha=1.8$ and $\alpha = 2$ (equation \ref{eq:paretodist}) plotted against a distribution at $\lambda = 0$. We see that they fit adequately with the higher end of the distribution, but not perfectly. The simple Pareto distribution becomes a straight line because of the logarithmic axes in the plot. The same figure also contains a parametrization of the wealth \footnote{This is done in the way Partriarca et al. (2004)\cite{Patriarca} does. A recipe is shown in appendix \ref{app:partriarca}}. Figure \ref{fig:paramfig2} also shows such a parametrization, but for a higher savings rate $\lambda=0.9$. The parametrisations are indicated by a label $P(x)$.

@@

\begin{figure}
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=\textwidth]{../figures/5ac/5cLOGLOG_N500_varSavings.pdf}
  \caption{}
  \label{fig:logdistribution}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{../figures/5ac/omega.pdf}
  \caption{}
  \label{fig:straightline}
\end{subfigure}
\caption{Logarithmic plot wealth distribution from figure \ref{fig:distribution} (right), and the logarithm of the Gibbs measure (equation \ref{eq:gibbs}) of every data point (right).}
\label{fig:logplot}
\end{figure}

\begin{figure}
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{../figures/5ac/5c_parameterization0.pdf}
  \caption{}
  \label{fig:paramfig1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{../figures/5ac/5c_parameterization09.pdf}
  \caption{}
  \label{fig:paramfig2}
\end{subfigure}
\caption{Parametrization of two different wealth distributions, $\lambda=0$ and $\lambda=0.9$. Method for parametrization is found in appendix \ref{app:partriarca}. For $\lambda=0$ two Pareto power law distributions are also shown.}
\label{fig:paramfig}
\end{figure}

%% Problem d.
\begin{figure}
\begin{subfigure}{.49\textwidth}
	\centering
	\includegraphics[width=\linewidth]{../figures/5d/5d_0-var-0.pdf}
	\caption{}
	\label{fig:neighbour1}
\end{subfigure}
\begin{subfigure}{.49\textwidth}
	\centering
	\includegraphics[width=\linewidth]{../figures/5d/5d_05-var-0.pdf}
	\caption{}
	\label{fig:neighbour2}
\end{subfigure}
\caption{Effect of neighbour-only interaction}
\end{figure}

\begin{figure}
\begin{subfigure}{.49\textwidth}
	\centering
	\includegraphics[width=\linewidth]{../figures/5d/5d_0-var-0-PARETO.pdf}
	\caption{}
	\label{fig:neighbourpareto1}
\end{subfigure}
\begin{subfigure}{.49\textwidth}
	\centering
	\includegraphics[width=\linewidth]{../figures/5d/5d_0-var-0-POWERLOG.pdf}
	\caption{}
	\label{fig:neighourpareto2}
\end{subfigure}
\caption{Effect of neighbour-only interaction}
\end{figure}

@@

\bibitem{Arnold} Arnold, B. C. (1983). 
	\emph{Pareto Distributions}.
	 International Co-operative Publishing House

@@

\begin{appendices}

\section{Parametrization from Patriarcal et al.}
\label{app:partriarca}
A corresponding exact solution of an income distributions for a generic value of $\lambda$ with $0<\lambda<1$ is provided in Patriarca et al.\cite{Patriarca}. Fir one employs the reduced variable
\begin{equation}
x = \frac{m}{\ev{m}}
\end{equation}
the agent money in units of average money $\ev{m}$ and the parameter
\begin{equation}
n(\lambda) = 1 + \frac{3\lambda}{1-\lambda}.
\end{equation}
The money distributions, for arbitrary values of $\lambda$, are well fitted by the function
\begin{equation}
P_n(x) = a_nx^{n-1}e^{-nx}
\end{equation}
where $a_n$ is a normalization factor shown to be
\begin{equation}
a_n = \frac{n^n}{\Gamma(n)}
\end{equation}
\end{appendices}
